Attractive people, Attractive jobs 

### 2024-04-16 paper/paper.qmd
Update paper.qmd

# Model

>>>>

```{r}
#| message: false
#| echo: false
#| label: fig-physical
#| fig-cap: Physical attractives .vs employment (2023)
cleaned_data <- select(cleaned_data)

cleaned_data %>%
  ggplot(mapping = aes(x = highlyattractive, y = higherstatusjob)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Highly Attractive vs. Higher Status Job in 2023",
    x = "Highly Attractive",
    y = "Employment"
  ) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic()
